\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-06-23 coqimpl.tex

Now that we know a family data structure is actually a list of compiled
modules, we may want to aggregate them into one complete compiled
module. We achieve that by repeatedly using Coq's "Include" command as
the example illustrated. Note that, in our example, we include two
functors without arguments---this is due to one of the feature of
"Include": non-instantiated parameters will be automatically
instantiated by the appropriate fields in the surrounding defining
module. The resulting module is just like mundane Coq's module and thus
enjoy all the computational mechanism from Coq for free.

@@

An inheritance data will be annotated with the type for the input family and output family, and generally there are three kinds of inheritance---extend, override and inherit. Extending corresponds to adding new fields, overriding corresponds to modify existent fields and inheriting corresponds to directly taking fields from the parent. Thus it is possible to consider inheritance as solely a data rather than a functor, and this actually provides us the possibility to \text{mix-in} inheritance data.

\textbf{Reasoning Requires Non-Overridable.} This compilation strategy can allow fields to have type dependent on former fields thus fulfilling \ref{langdesign-req1}. However, there are some caveats, especially when the former fields are actually ``proof-relevant''. For example, we may define $"add" : \mathbb{Z} \to \mathbb{Z} \to \mathbb{Z}$ as one field and intends to prove its commutativity in a following field $"comm"$. But to prove so, we need to know more than just a type interface of $"add"$ but also its \textbf{concrete definition}. Otherwise, in the future, once $"add"$ is overridden into a subtraction function then $"comm"$ will have problem to be  inherited. A more concrete example is in \cref{fig:plugin-example1}, consider the case we have "Field b : self_A.a = 1 := .." instead, then our compilation and Coq's type check will both fail: in the context of "b" (module type "a_6") we only know "a" is of type nat but nothing more (and this is necessary so that "a" can be overridden in the future). To fix that, we need more information on "a" than its type---we need to expose its concrete definition "a = 1" to appear in the context of "b".

To achieve such exposure of definition, in meta-theory we only need to expose the information as propositional equality as part of the signature, and in our Coq plugin, we can achieve that even easier by exposing the whole definition directly into module type. Doing so we can have a better judgemental equality and we prohibit overriding because subtraction doesn't have the same definition as $add$. We require the users to decorate field as `Final' so that the plugin will proceed with this special treatment.

>>>>

Now that we know a family data structure is actually a list of compiled
modules, we may want to aggregate them into one complete compiled
module. We achieve that by repeatedly using Coq's "Include" command as
the example illustrated. Note that, in our example, we include two
functors without arguments---this is due to a perculiarity of Coq's
"Include": non-instantiated parameters will be automatically
instantiated by the appropriate fields in the surrounding defining
module.\YZ{'For example, ...'}
The resulting module is just like mundane Coq's module and thus
enjoy all the computational mechanism from Coq for free.

@@

An inheritance data will be annotated with the type for the input family
and output family, and generally there are three kinds of
inheritance---extend, override and inherit. Extending corresponds to
adding new fields, overriding corresponds to modifying existent fields,
and inheriting corresponds to directly taking fields from the parent.
Thus, it is possible to consider inheritance as solely a data rather than
a functor, and this actually provides us the possibility to
\text{mix-in} inheritance data.

\textbf{Reasoning Requires Non-Overridable.} This compilation strategy
can allow fields to be type-dependent on former fields thus fulfilling
\ref{langdesign-req1}. However, there are some caveats, especially when
the former fields are actually ``proof-relevant''. For example, we may
define $"add" : \mathbb{Z} \to \mathbb{Z} \to \mathbb{Z}$ as one field
and intend to prove its commutativity in a following field $"comm"$.
But to prove so, we need to know more than just a type interface of
"add" but also its \textbf{concrete definition}. Otherwise, in the
future, once "add" is overridden into a subtraction function then
"comm" will have problem to be inherited.
A more concrete example is in \cref{fig:plugin-example1}, consider the
case we have "Field b : self_A.a = 1 := .." instead. Then our
compilation and Coq's type checking will both fail: in the context of
"b" (module type "a_6") we only know "a" is of type "nat" but nothing
more (and this is necessary so that "a" can be overridden in the
future). To fix that, we need more information on "a" than its type---we
need to expose the concrete definition "a = 1" to the context of "b".
\YZ{I had a hard time working through these two paras. I guess they are
saying that there is a need to expose definitional equalities, and
therefore we need non-overridables. This causal flow should be made
more explicit.}

To achieve such exposure of definition, in meta-theory we only need to
expose the information as propositional equality as part of the
signature, and in our Coq plugin, we can achieve that even easier by
exposing the whole definition directly into module type. Doing so we can
have a better judgemental equality and we prohibit overriding because
subtraction doesn't have the same definition as $add$. We require the
users to decorate field as `Final' so that the plugin will proceed with
this special treatment.\YZ{This para is confusing: which kind of equality is used, propositional or judgmental? Where does 'Final' show up in the example?}
